\Large \bf CS380S: Project Update

### 2018-10-29 update/update.tex
Continued working on update, left TODO for things that are blatantly missing

Given two versions $P_1, P_2$ of the same program P, we propose a relational verification for the entropy of the cryptographic values in the program. By introducing the concept of ``differential taint analysis'', we hope to produce a product program $P_1 \times P_2$ that is semantically equivalent to the sequential composition $P_1; P_2$, but such that we can prove useful safety properties of $P_1 \times P_2$ that would be difficult to prove with standard techniques on $P_1$, $P_2$, or $P_1; P_2$.

\section{Motivating Example}

@@

where $f$ is some complex function that is difficult to reason about, but does not change between $P_1$ and $P_2$. Then, safety properties about the entropy of the cryptographic values in $c$ would hold in both programs or in neither program.

\section{Existing Techniques}

@@

Under-approx tools don't exist (why do we need under approx tools?), and also difficult to reason about arbitrary functions (but they are usually irrelevant to the analysis you're performing), also can't just run taint analysis on one program because don't know what the taint results should look like (the old program gives us a correctness criteria/oracle to infer what the correct taint results would be).

\section{Our Approach}
Introduce concept of differential taint analysis here. Talk about constructing a product program.

@@

Note that, during the construction of the product program, we need to be able to merge the if statements in the two programs. Also note that we need to demonstrate set equality between the taint for $s_1, s_2$ when they are used in the if statement.

\section{What We Hope To Show}
Talk about how we assign the output of a sufficiently entropic value to a variable in $P_1$ iff we also assign it in $P_2$. Then show that there is an equivalence in the taint propagation (prove set equality of the places where cryptographic values are used).

\section{Real World Applications}
How our analysis framework would be able to identify real world bugs. What are the benchmarks we compare against (OpenSSL, FreeBSD, etc.).

>>>>

Given two versions $P_1, P_2$ of the same program P, we propose a relational verification for the entropy of the cryptographic values in the program. By introducing the concept of ``differential taint analysis'', we hope to produce a product program $P_1 \times P_2$ that is semantically equivalent to the sequential composition $P_1; P_2$, but such that we can prove useful safety properties of $P_1 \times P_2$ that would be difficult to prove with standard techniques on $P_1$, $P_2$, or $P_1; P_2$. The safety property we are the most interested in proving is that cryptographic values rely on sufficiently many bits of entropy when they are used.

\section{Example Formalization}

@@

where $f$ is some complex function that is difficult to reason about, but does not change between $P_1$ and $P_2$. Then, clearly, our safety properties about the entropy of the cryptographic values in $c$ would hold in both programs or in neither program.

\section{Existing Techniques, DTA Motivation}

@@

Standard taint analysis will under/overapproximate the taint, so we may not be able to use it to directly prove our safety property on the target program. Thus, we can leverage the approach of relational verification.

Relational verification aims to solve this problem by proving relational properties between two programs. However, the naive relational verification approach of verifying each program individually is infeasible given arbitrarily difficult-to-reason-about functions even if those functions do not change between versions of the program. One approach is to underapproximate the taint on one program and overapproximate the taint on another program to verify the set equality of taint sources, but this still falls prey to the approximation of taint analysis given arbitrarily complex functions. Also, current tooling does not widely support underapproximating taint analysis.

Finally, even with a sufficiently precise taint analysis, it is unclear how to determine the ``correct'' set of sources a cryptographic value should rely on at any point in the program. For example, some programs will use weak entropy on system startup, and increase the entropy in those values, later on. Thus, by running our analysis on two versions of the program, we can use one version as an oracle for the correctness criteria of the other program. In other words, we can use it to infer what the set of taint results should be for any variable at any point in the program.

\section{Our Approach}
Given the two programs in the example, we propose generating a product program similar to the following:

@@

Note that, during the construction of the product program, we need to be able to merge the if statements in the two programs.

We would like to demonstrate set equality between the taint for $s_1, s_2$ when they are used in the if statement, which amounts to demonstrating the equivalence of the taint propagation through the program. We would also like to demonstrate that we assign the output of a sufficiently entropic value to a variable in $P_1$ if and only if we also assign it that sufficiently entropic value in $P_2$.

Proving these two properties (set-equality and equivalence of assignments) allows us to claim that $P_1$ has the safety property if and only if $P_2$ has the safety property.

\section{Real World Applications}

A verification tool like this could be especially useful for a maintainer of a project that relies on cryptographic values. For example, if she audits her code once to confirm that it uses entropy properly, she can use differential taint analysis on future commits to confirm that the new code does not introduce this class of bugs.

How our analysis framework would be able to identify real world bugs. What are the benchmarks we compare against (OpenSSL, FreeBSD, etc.). What are the projects we will evaluate the tool on. %TODO
